String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-10-19 2023-1-19/sections/cefa.tex
remove some contents

The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$ is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states. Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$). Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$ where 
\begin{itemize}
\item $R' = R_1 \cup R_2 \cup \{r'_1, r'_2\}$, $Q' = Q_1 \cup Q_2 \cup \{q'_0\}$ with $q'_0 \not \in Q_1 \cup Q_2$, $I' = \{q'_0\}$, 
%
\item $\delta'$ is the union of four transitions sets:
\begin{itemize}
  \item $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$
  \item $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$
  \item $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid q_1\not\in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$
  \item $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid q_2\not\in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$
\end{itemize}
 where $(\myvec{v_1}, \myvec{0}, 1,0)$ is a vector that updates $R_1$ by $\myvec{v_1}$, updates $R_2$ by $\myvec{0}$, and updates $r'_1,r'_2$ by $1,0$ respectively. Similarly for $(\myvec{0}, \myvec{v_2}, 0, 1)$, and so on.

>>>>

The \emph{union} of $\aut_1$ and $\aut_2$ is denoted by $\aut_1 \cup \aut_2$. Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$). Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$ where 
\begin{itemize}
\item $R' = R_1 \cup R_2 \cup \{r'_1, r'_2\}$, $Q' = Q_1 \cup Q_2 \cup \{q'_0\}$ with $q'_0 \not \in Q_1 \cup Q_2$, $I' = \{q'_0\}$, 
%
\item $\delta'$ is the union of four transitions sets:
\begin{itemize}
  \item $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$
  \item $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$
  \item $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid q_1\not\in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$
  \item $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid q_2\not\in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$
\end{itemize}
 where $(\myvec{v_1}, \myvec{0}, 1,0)$ is a vector that updates $R_1$ by $\myvec{v_1}$, updates $R_2$ by $\myvec{0}$, and updates $r'_1,r'_2$ by $1,0$ respectively. Similarly for $(\myvec{0}, \myvec{v_2}, 0, 1)$, and so on.
